Brief Article

### 2021-08-19 Draft.tex
added bib files and 5 references

@@

>>>>

Effects of a hybrid interface and multimodal features for learning how to program \cite{unal2021effects, grafsgaard2014additive}.

Benefits of a textual versus graphical interfaces for learning how to program \cite{dillon2012comparing}.

Predicting user frustration and measuring perceived cognitive load \cite{feild2010predicting, hart1988development}.

@@

%Sets the bibliography style to UNSRT and imports the 
%bibliography file "samples.bib".
\bibliographystyle{acm}
\bibliography{references}
